### 2023-10-18 vesicle_code/docs/confinedMulti/response.tex

%%%%%%%%
\item Please define whether $\mathbf{n}$ in Eq.~(12) is the inward or outward pointing unit normal.

\noindent
{\bf Response:} It is the outward pointing unit normal.  We have adjusted the text to clarify this.

%%%%%%%%
\item How is surface incompressibility enforced?

\noindent
{\bf Response:} The surface incompressibility is enforced via the tension $\sigma$ (Eq.~(6)) in the original manuscript), 
which is a Lagrange multiplier so that the inextensibility condition can be satisfied. We adjusted the text in the revision to make this clearer.

@@

%%%%%%%%
\item The authors mention the phrase `size of lubrication layer' in the
  paper. They need to explicitly define this parameter. It could be
    confusing to a reader whether they talk about
    $|\gamma_{\mathrm{layer}}|$ or $w_{\mathrm{top}}$ and
    $w_{\mathrm{bottom}}$.

\noindent
    {\bf Response:} We have labelled $w_{\mathrm{top}}$ and
    $w_{\mathrm{bot}}$ in Figure 1. We have adjusted the text in Section
    2.4.

%%%%%%%%
\item The authors measure the tangential velocity at 4 points. They
  should provide some justification for this number. Also, it is
    advisable that in Figure 7, the authors use a different color for
    each velocity plot. The plot looks highly convoluted and does not
    convey the message clearly. Also, what are the bounds within which
    the authors call the tangential velocity to be constant in Figure 7?
    They should define a bound for the variation that could be
    considered constant. Moreover, in Figure 7, for the floppy vesicle,
    the authors see a large deviation for the tangential velocity. It
    doesn't seem like the velocity could be called `constant'. The
    authors should provide a more detailed explanation for this.

\noindent
    {\bf Response:} We calculated the tangential velocity of all $N =
    1024$ Lagrangian points for each of the three cases. Plotting all
    1024 lines in the manuscript would be uninformative. To prove this is
    the case, a plot of 32 of the tangential velocities is in Figure~\ref{fig:tangVel} of this document. 
%    
    Instead we track the tangential velocity of each Lagrangian marker on the vesicle membrane, measuring the variation in this tangential velocity over the duration when the vesicle is inside the stenosis. This variation over time gives a ``spread in tangential velocity" on each marker, and we color-code the membrane by this spread in tangential velocity scaled to the velocity magnitude. For a tank-treading vesicle, this scheme would give a membrane of a uniform color. On the other hand, a non-uniformly colored membrane implicates the lack of tank-treading in the vesicle membrane, which may also correspond to significant deformations in the membrane.
%   
% Instead, in the document,
%  we report the average tangential velocity in the region $x \in
% [4,10]$, and report the spread of all tangential velocities from
%this mean value. 
More quantitatively, if this spread is less than 15\%, we would
    characterize this as a tank-treading vesicle. Their spread is 1.2\%
    for the stiff single-component vesicle, 12\% for the multicomponent
    case, and 313\% for the floppy single-component case. Therefore, the
    floppy single-component vesicle is not tank-treading, while the
    other two cases are tank-treading. We have made this clear in the
    text.
%    {\bf TODO: Change color of Fig 7 lines or state why we don't do
%    this.}

@@

%%%%%%%%
\item Page 2, left column : the flow is assumed to be in the limit of
  zero Reynolds number : not the fluid

\noindent
{\bf Response:} Thank you for correcting this error. We have added the
word `flow' to the manuscript.

%%%%%%%%
\item The title is a bit misleading as the authors only consider the
  deflation equal to the one of RBC. However, as there is some conflict
  between capsules and vesicles as models of RBC, the title can be
  tolerated.

\noindent
{\bf Response:} We thank the referee for this comment. We did not change the title as the referee found the title tolerable.
\end{enumerate}

### 2023-10-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
starting on new Fig 7 plots

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. Also illustrated is the vesicle shape and the four
  Lagrangian points at the location indicated by the dash line. The
  black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}

>>>>

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SC_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SCp55_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/MCp5_treading_velocity2.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. 
  \textcolor{blue}{
  Also illustrated is the vesicle shape when its center of mass is
  located at $x=4$. Then, color represents the spread of the tangential
  velocity relative to the mean tangential velocity, where the average
  is taken over the region $x \in [4,10]$. 
  }
%  Also illustrated is the vesicle shape and the four
%  Lagrangian points at the location indicated by the dash line.
  The black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}
